Cover letter for the original IJRR submission

### 2017-12-12 body/appendix_algo.tex
algo 2

From the start configuration, given as an input by the user,
we create the initial state $s0$.
Algorithm~\ref{alg:interpolate}  is then called with $s0$, as well as the discretized path 
$\mathbf{Q}^0$, as input parameters.

\begin{algorithm}[!tbp]
\caption{Discretization of a path} \label{interpolate}
	\begin{algorithmic}[1]
	%~ \Function{GenerateConfiguration}{}
	\Function{Interpolate}{$s0$,$\mathbf{Q}^0$, $MAX\_TRIES$}
		\State $states \gets (s0)$ \Comment{List of states intialized with $s0$}
		\State $nb\_fail \gets 0$ 
		\State $i \gets 1;$ \Comment{Current index in the list}
		\While {$i < length(\mathbf{Q}^0)$}
			\State $pState \gets last\_element(states)$
			\State $s \gets$ \textsc{GenFullBody}$(pState, element(\mathbf{Q}^0,i))$
			\If {$s \not= 0 $}
				\State $nb\_fail \gets 0$
				\State $i \gets i+1$
				\State \textbf{return} $\mathbf{q}^{0}$
			\Else
				\State $nb\_fail \gets nb\_fail + 1$
				\If {$nb\_fail == MAX\_TRIES$}
					\State \textbf{return} $FAILURE$
				\EndIf				
				\State $s \gets $\textsc{IntermediateContactState}$(pState)$
			\EndIf
			\State $push_back(states, s)$
		\EndWhile
		\State \textbf{return} $states$
	\EndFunction
\end{algorithmic}
\label{alg:interpolate}
\end{algorithm}

@@

\begin{algorithm}[!tbp]
\caption{Full body contact generation method} \label{interpolate}
	\begin{algorithmic}[1]
	%~ \Function{GenerateConfiguration}{}
	\Function{\textsc{GenFullBody}}{$pState$,$\mathbf{q}^0$}
		\State State $newState$
		\State $newState.q0 = \mathbf{q}^0$
		\State $newState.freeLimbs = pState.freeLimbs$
		\State /*First try to maintain previous contacts*/
		\State $nbContactsBroken = 0$
		\For {\textbf{each} Limb $k$ in $pState.contactLimbs$}
			\If {$!$\textsc{MaintainContact}$(pState,\mathbf{q}^0,k)$}
				\State $nbContactsBroken += 1$
				\If {$nbContactsBroken > 1$}				
					\State \textbf{return} $NULL$
				\EndIf				
				\State $push(newState.freeLimbs,k)$
			\Else 					
				\State $push(newState.contactLimbs,k)$
			\EndIf
		\EndFor
		\For {\textbf{each} Limb $k$ in $pState.freeLimbs$}
			\If {\textsc{GenerateContact}$(\mathbf{q}^0,k)$}	
				\State $push(newState.contactLimbs,k)$
				\State $remove(newState.freeLimbs,k)$		
				\State \textbf{return} $newState$
			\EndIf
		\EndFor
		\If {\textsc{IsInStaticEquilibrium}$(newState)$}
			\State \textbf{return} $newState$
		\Else
			\State \textbf{return} $NULL$
		\EndIf
	\EndFunction
\end{algorithmic}
\label{alg:pi}
\end{algorithm}

@@

The method \textsc{IsInStaticEquilibrium} returns whether a given state is in static equilibrium.

>>>>

From the start configuration, given as an input by the user,
we create the initial state $s0$. A state is described by a whole-body configuration, as well as the list of currently active contacts.
Algorithm~\ref{alg:interpolate}  is then called with $s0$, as well as the discretized path 
$\mathbf{Q}^0$, as input parameters.

\begin{algorithm}[!tbp]
\caption{Discretization of a path} \label{interpolate}
	\begin{algorithmic}[1]
	%~ \Function{GenerateConfiguration}{}
	\Function{Interpolate}{$s0$,$\mathbf{Q}^0$, $MAX\_TRIES$}
		\State $states \gets (s0)$ \Comment{List of states intialized with $s0$}
		\State $nb\_fail \gets 0$ 
		\State $i \gets 1;$ \Comment{Current index in the list}
		\While {$i < length(\mathbf{Q}^0)$}
			\State $pState \gets last\_element(states)$
			\State $s \gets$ \textsc{GenFullBody}$(pState, element(\mathbf{Q}^0,i))$
			\If {$s \not= 0 $}
				\State $nb\_fail \gets 0$
				\State $i \gets i+1$
				\State \textbf{return} $\mathbf{q}^{0}$
			\Else
				\State $nb\_fail \gets nb\_fail + 1$
				\If {$nb\_fail == MAX\_TRIES$}
					\State \textbf{return} $FAILURE$
				\EndIf				
				\State $s \gets $\textsc{IntermediateContactState}$(pState)$
			\EndIf
			\State $push\_back(states, s)$
		\EndWhile
		\State \textbf{return} $states$
	\EndFunction
\end{algorithmic}
\label{alg:interpolate}
\end{algorithm}

@@

\begin{algorithm}[!tbp]
\caption{Full body contact generation method} \label{interpolate}
	\begin{algorithmic}[1]
	%~ \Function{GenerateConfiguration}{}
	\Function{\textsc{GenFullBody}}{$pState$,$\mathbf{q}^0$}
		\State $newState \gets create\_state(q0, FreeLimbs(pState))$
		\State /*First try to maintain previous contacts*/
		\State $nConBroken \gets 0$
		\For {\textbf{each} $k$ in $ContactLimbs(pState)$}
			\If {$!$\textsc{MaintainContact}$(pState,\mathbf{q}^0,k)$}
				\State $nConBroken \gets nConBroken +1$
				\If {$nConBroken > 1$}				
					\State \textbf{return} $0$
				\EndIf				
				\State $add\_free\_limb(newState,k)$
			\Else 					
				\State $add\_contact\_limb(newState,k)$
			\EndIf
		\EndFor
		\For {\textbf{each} $k$ in $FreeLimbs(pState)$}
			\If {\textsc{GenerateContact}$(\mathbf{q}^0,k)$}	
				\State $add\_contact\_limb(newState,k)$
				\State \textbf{return} $newState$
			\EndIf
		\EndFor
		\If {\textsc{IsInStaticEquilibrium}$(newState)$}
			\State \textbf{return} $newState$
		\Else
			\State \textbf{return} $0$
		\EndIf
	\EndFunction
\end{algorithmic}
\label{alg:pi}
\end{algorithm}

@@

The method \textsc{IsInStaticEquilibrium} returns whether a given state is in static equilibrium.
$ContactLimbs$ (respectively $FreeLimbs$) returns the list of limbs that are in contact (respectively \textit{not} in contact) at a given state. $add\_contact\_limb$ (respectively $add\_free\_limb$)  marks a limb as in contact (respectively \textit{not} in contact) at a given state.
%~ $add\_contact\_limb(newState,k)$ marks a limb as in contact at a given state.
